Percolation Analysis – Building a Package

### 2019-08-01 paper.Rmd
alle scripte bis auf mapping in eine funktion

# create df from input data set
data <- read.csv("source_data/BefundesNL-minimal.csv", sep = ",") #' crazy mistakes happen if this is wrong...
#' This file needs three columns: PlcIndex, Easting, Northing in this order.
#' Additional fields Lat Long not used for this program.
#' Note that the Easting and Northing need to be UK grid references with the Alphabetic
#'  grid square converted to a numeric prefix for each
#' List any entries with null values and write to file

@@

source("R/cluster_frequency_script.v2.17.R")
clusterFrequency()

>>>>

# create df from input data set
data <- read.csv("raw_data/BefundesNL-minimal.csv", sep = ",") #' crazy mistakes happen if this is wrong...
#' This file needs three columns: PlcIndex, Easting, Northing in this order.
#' Additional fields Lat Long not used for this program.
#' Note that the Easting and Northing need to be UK grid references with the Alphabetic
#'  grid square converted to a numeric prefix for each
#' List any entries with null values and write to file

@@

source("R/cluster_frequency_script.v2.17.R")
clusterFrequency(radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20)
